Large-scale harmonic patterns clustering

### 2010-03-12 Paper/Paper.tex
were up-to-date

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan? is Juan on? is Graham on?

@@

Other large-scale work use summarization of the features. We mention 
gaussian mixtures \cite{Mandel2005}, aggregate features \cite{Bergstra2006a}
and linear dynamical systems \cite{Barrington2009a}. The chroma representation
is close from an harmonic point of view to the actual music, in particular
we can ``listen'' to the patches (see Section \ref{sec:experiments}).
This is an advantage for analyzing a large data set, thus
we restrain ourselves from using generative models to compress our features.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939        0.066079
% code 10       0.161812        0.045690
% code 50       0.147472        0.038456
% code 100      0.142194        0.036725
% code 200      0.137548        0.033923
% code 500      0.131211        0.

@@

>>>>

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan? is Graham on?

@@

Other large-scale work use summarization of the features. We mention 
gaussian mixtures \cite{Mandel2005}, 
aggregate features \cite{Bertin-Mahieux2008}
and linear dynamical systems \cite{Barrington2009a}. 
The advantage of \textit{Shingles} representation (stacked chroma vectors)
is that it is close from an harmonic point of view to the actual music, 
in particular
we can ``listen'' to the patches (see Section \ref{sec:experiments}).
This is an advantage for analyzing a large data set, thus
we restrain ourselves from using generative models to compress our features.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939        0.066079
% code 10       0.161812        0.045690
% code 50       0.147472        0.038456
% code 100      0.142194        0.036725
% code 200      0.137548        0.033923
% code 500      0.131211        0.030973

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|c||c|}
\hline
\# codes & \# bars & full data & codebook & test set \\ \hline \hline
10 & 1 & $$ & $$ & \\ \hline
20 & 1 & $$ & $$ & \\ \hline
10 & 2 & $\bf{1774788}$ & $$ & $1782164$\\ \hline
20 & 2 & $$ & $$ & \\ \hline
\end{tabular}
\end{center}
\caption{{Encoding error of the test data set using NMF basis learned
on the whole data and on the codebook. We also encode the test set
directly to give us an upper bound.}}
\label{tab:nmf}
\end{table}
% RESULTS:         whole data             codebook     test set
%10 codes 2 bars   1774788.2566 (200 it)               1739639.7304 (1000 it)
%10 codes 1 bar
